<!-- howto_fva.md is generated from howto_fva.Rmd. Please edit that file -->

# Install rPython-win
Install rPython-win following 
[these instructions](https://github.com/cjgb/rPython-win)
with the current (May 2017) python setup at fvafr. 
Assuming you have installed R and Rtools from the software shop, you can run:

```{r, eval = TRUE, echo = FALSE, comment = ""}
cat(readLines(file.path("codes", "windows_install_rpython-win.R")), sep = "\n")
```
To date you need to use R 3.2.5 for this to work since our Rtools version is out
of date and does not work for our current R installation. 
Run "C:\Program Files\R\R-3.2.5\bin\x64\Rgui.exe" from a command prompt, set the 
R version used by RStudio to 3.2.5 or 
navigate to "C:\Program Files\R\R-3.2.5\bin\x64" and start Rgui.exe.

# Install excerptr

Get the excerptr source from 
[github](https://github.com/fvafrCU/excerptr), 
edit the file DESCRIPTION by removing the line reading
    OS_type: unix
and inserting your R version and install the package manually:
```{r, eval = TRUE, echo = FALSE, comment = ""}
cat(readLines(file.path("codes", "windows_install_excertpr.R")), sep = "\n")
```

# Run excerptr and pandoc on a Windows machine at fvafr

At fvafr, pandoc is not configured to find [pdf]latex, for reasons beyond my 
reach.
So we have to set the pandoc output format to html:
```{r, eval = TRUE, echo = FALSE, comment = ""}
cat(readLines(file.path("codes", "pandoc_at_fvafr.R")), sep = "\n")
```


