<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Build Status](https://travis-ci.org/fvafrCU/excerptr.svg?branch=master)](https://travis-ci.org/fvafrCU/excerptr)
[![Coverage Status](https://codecov.io/github/fvafrCU/excerptr/coverage.svg?branch=master)](https://codecov.io/github/fvafrCU/excerptr?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/excerptr)](https://cran.r-project.org/package=excerptr)

# excerptr
This is an R interface to [excerpts](https://pypi.python.org/pypi/excerpts).

## Introduction

Please read the [vignette.](http://htmlpreview.github.io/?https://github.com/fvafrCU/excerptr/blob/master/inst/doc/excerptr_Introduction.html)

<!-- vignette. Either [the version on github](http://htmlpreview.github.io/?https://github.com/fvafrCU/excerptr/blob/master/inst/doc/excerptr_Introduction.html)
or [the one released on cran](https://cran.r-project.org/packages=excerptr/vignettes/excerptr_Introduction.html). -->

Or, after installation, the help page:
```{r, eval = FALSE}
help("excerptr-package", package = "excerptr")
```
```{r, echo = FALSE}
  package <- "excerptr"
  topic <- "excerptr-package"
  help_file <- utils:::.getHelpFile(help(topic, package = (package)))
  captured <- gsub('_\b', '',  capture.output(tools:::Rd2txt(help_file) ))
  cat(captured, sep="\n")
```

## System Requirements
excerptr needs [python3](https://www.python.org/download/releases/3.0/).

## Installation

### Unix
Install [the rPython package](https://cran.r-project.org/package=rPython), see 
file [INSTALL](https://cran.r-project.org/package=rPython/INSTALL) there,
<!-- then install excerptr from [CRAN](https://cran.r-project.org/package=excerptr) -->
then install excerptr from [CRAN](https://cran.r-project.org/)
```{r, eval = FALSE, results = "hide"}
install.packages("excerptr")
```

### Windows
Install [rPython-win](https://github.com/cjgb/rPython-win)
(follow the instructions at 
[https://cran.r-project.org/package=rPython/INSTALL](https://cran.r-project.org/package=rPython/INSTALL)
).
Then get the excerptr source
from [github](https://github.com/fvafrCU/excerptr), edit the file DESCRIPTION and remove the line reading
    OS_type: unix
and install the package manually:
```{r, eval = FALSE, results = "hide", message = FALSE}
local_directory <- tempdir()
local_path <- file.path(local_directory, "master.zip")
url <- "https://github.com/fvafrCU/excerptr/archive/master.zip"
download.file(url, local_path, method = "wininet", mode = "wb")
unzip(local_path, exdir = local_directory)
excerptr_path <- file.path(local_directory, "excerptr-master")
description <- file.path(excerptr_path, "DESCRIPTION")
my_r_version <- paste(R.Version()[["major"]], R.Version()[["minor"]], sep = ".")
d <- readLines(description)
d1 <- d[-grep("^OS_type:", d)]
d1[grep("^ *R \\(", d1)] <- paste0("    R (>= ", my_r_version,")")
writeLines(d1, description)
install.packages(excerptr_path, repos = NULL, type = "source")
```

